%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter 5: Summary and Conlusions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

From a few years to now, it has had a enourmous growth of Version Control tools. It has become in an indispensable tool in the software development methodologies and all the teaching institutions know that incorporing them to their education systems is fundamental to providing a quality service.
\bigskip

Ésto es lo que se pretende con la herramienta obtenida tras la realización de este Trabajo de Fin de Máster: que sea posible su implantación dentro del marco académico de la Universidad de La Laguna, partiendo de la premisa de que, actualmente, el desarrollo de un proyecto software sin tener detrás un sistema de control de versiones, no es viable.
\bigskip

This is what is intended with the developed tool after the completion of this Master's Degree Final Project: that it would be deployed at University of La Laguna basing on the premise that, currently, the development of a software project without using a version control system, is not viable. 
\bigskip

The automation of cloning and execution tasks would facilitate, in first instance, the students' projects correction. The amount of saved time per the teacher is considarable, keeping in mind the large amount of practices of each student per subject. This huge teacher's workload could be use in another academic scopes.
\bigskip

By the other hand, this tool set the bases to future improvements, like enlarge the functionalities of it. It has been developed thinking about the scalability and, since it has all the structure created (user's authentication, cloning, execution and reporting), it's possible to add improvements without too effort.
\newpage

In conclusion, we can affirm that all the goals established at the beggining of the subject have been fulfilled and the next development guidelines could be:


\begin{itemize}
	\item Extend the tool's GitHub functionalities:
	\begin{itemize}
		\item To push changes to the repositories (git push).
		\item Create issues.
		\item Manage Pull Requests.
		\item Search repositories.
		\item Organizations and repositories' permissions management.
		\item Manage Classrooms.
	\end{itemize}
	\item Improve the reporting documentation generated.
	\item Perform local deployment of web applications (like child process of the tool).
\end{itemize}

